\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-08-09 paper/paper.tex
intro done

Ultra-stabilized spectrographs like \HARPS\ \todo{(define \& cite)}
predominantly utilize a cross-correlation method with a custom-built
list of spectral lines (see e.g. Queloz1995, Baranne1996).
A lesser-used alternative is cross-correlation or maximum-likelihood
fitting using a template spectrum generated from the data \todo{(Buchhave,
Anglada-Escude)}.
This often involves masking or downweighting of the most
telluric-contaminated spectral regions.
As an alternative, gas-cell-calibrated spectrographs like
\HIRES\ \todo{(CITE)} commonly adopt more of a forward-modeling approach.
In this framework, the instrumental line spread function, the stellar
RV, and other parameters are optimized by modeling each observation as
a combination of shifted and instrument-convolved template spectra for
the star and gas cell (CITE).
Here we focus on the ultra-stabilized spectrograph hardware, but consider
a few different data-analysis approaches.
Most of what we do here could be generalized to data generated by gas-cell hardware.

\todo{HOGG: syntactical reference}

For the purposes of this work, we assume that our data set consists of multiple observations of the same star with good coverage throughout the observing season, so that we have seen the star many times spanning the range of telluric-to-star relative RV shifts. 
This means we are not considering the case of a real-time data reduction pipeline. 
We also assume a \HARPS-like setup, i.e. no absorption cell, but the points we make can be easily generalized to the gas-cell case. 
We return to this point in the discussion \todo{(do this)}.

>>>>

Ultra-stabilized spectrographs like \HARPS\ \todo{(define \& cite)}
predominantly utilize a cross-correlation method with a custom-built
list of spectral lines (see e.g. Queloz1995, Baranne1996).
A lesser-used alternative is cross-correlation or maximum-likelihood
fitting using a template spectrum generated from the data \todo{(Buchhave,
Anglada-Escude)}.
This often involves masking or downweighting of the most
telluric-contaminated spectral regions.
As an alternative, gas-cell-calibrated spectrographs like
\HIRES\ \todo{(CITE)} commonly adopt more of a forward-modeling approach.
In this framework, the instrumental line spread function, the stellar
RV, and other parameters are optimized by modeling each observation as
a combination of shifted and instrument-convolved template spectra for
the star and gas cell (CITE).
Here we focus on the ultra-stabilized spectrograph hardware, but consider
a few different data-analysis approaches.
Most of what we do here could be generalized to data generated by
gas-cell hardware; we will return to this point in the discussion.

For the purposes of this \documentname, we will assume that the data
set at hand consists of multiple observations of the same star with
good coverage throughout the observing season.
We will assume that the resolution of the spectrograph is $(\lambda /
\Delta\lambda) > 30,000$, and the star is not near the ecliptic pole,
so that the observing coverage also delivers significant RV shifts
between star and atmosphere (and hence between star and tellurics).
We are not onsidering the case of a real-time data reduction pipeline,
because such a real-time pipeline does not, at the beginning of an
observing campaign, have many epochs at hand.
